Title

### 2015-12-09 paper/paper.tex
WIP: hashing out System Architecture and subsections

\section{System Architecture}
\subsection{Subgraph Selection}
\subsection{Subgraph Ordering}

>>>>

\section{System Architecture}

From a high level, our system is a pipeline, which takes an AMR representation
of the information set that is to be communicated as input, and outputs a set
of AMR representations, which are the AMRs representing the sentences
containing all of the information in the information set.

To accomplish this task, we split the problem into two subproblems: (1)
subgraph selection and (2) subgraph ordering.

\subsection{Subgraph Selection}

Subgraph selection solves the problem of splitting an AMR graph into a set of
subgraphs which are optimal by some criterion, such that the union of the
subgraphs is the original graph. Said more plainly, the problem is to split a
concept graph into sentences, such that emitting all of the sentences would
communicated all of the concepts in the original graph.

\subsection{Subgraph Ordering}

Subgraph ordering solves the problem of ordering a set of AMR sentences.
